The Country-level Impact of Educational Features on the Rate of Entrepreneurship - Data Gathering and Analysis

### 2014-11-13 GEMDataSource.Rmd
Updated regression output table and attempted simulation

# Library Repmis, Tidy, Reshape2, and plyr packages
library(repmis)
library(tidyr)
library(reshape2)
library(plyr)
library(WDI)
library(stargazer)

@@

# Run a linear regression
R1 <- lm(PercentIntention ~ PercentPerceived + PercentFear + AnnualGDPGrowth + 
           PercentOpportunities, data = CompleteDataset)
summary(R1)

# Calculate confidence intervals
confint(R1)

# Run a linear regression
R2 <- lm(PercentNascent ~ PercentPerceived + PercentFear + AnnualGDPGrowth, data = CompleteDataset)

R2 <- lm(PercentNascent ~ PercentPerceived + PercentFear + AnnualGDPGrowth + 
           PercentOpportunities, data = CompleteDataset)

summary(R2)

# Calculate confidence intervals
confint(R2)

# Run a linear regression
R3 <- lm(PercentOwner ~ PercentPerceived + PercentFear + AnnualGDPGrowth, data = CompleteDataset)

R3 <- lm(PercentOwner ~ PercentPerceived + PercentFear + AnnualGDPGrowth + 
           PercentOpportunities, data = CompleteDataset)

summary(R3)

# Calculate confidence intervals
confint(R3)

@@

```{r echo = FALSE, cache=TRUE, include=TRUE, results='asis'} 
# Create regression output table
labels <- c('Percent Perceived', 'Percent Fear',
            'Annual GDP Growth', 'Percent Opportunities', '(Intercept)')

@@

@@

>>>>>>> d492a8dcde27e8a4480f0504d410e52e7c2d7e6e

>>>>

# Library Repmis, Tidy, Reshape2, and plyr packages
library(repmis)
library(tidyr)
library(reshape2)
library(plyr)
library(WDI)
library(stargazer)
library(Zelig)

@@

# Run a linear regression
R1 <- lm(PercentIntention ~ PercentPerceived + PercentFear*PercentOpportunities + AnnualGDPGrowth, data = CompleteDataset)

# Obtain summary statistics of R1
summary(R1)

# Calculate confidence intervals of R1
confint(R1)

# Run a linear regression of R2
R2 <- lm(PercentNascent ~ PercentPerceived + PercentFear*PercentOpportunities + AnnualGDPGrowth, data = CompleteDataset)

# Obtain summary statistics of R2
summary(R2)

# Calculate confidence intervals of R2
confint(R2)

# Run a linear regression of R3
R3 <- lm(PercentOwner ~ PercentPerceived + PercentFear*PercentOpportunities + AnnualGDPGrowth, data = CompleteDataset)

# Obtain summary statistics of R3
summary(R3)

# Calculate confidence intervals of R3
confint(R3)

@@

```{r echo = FALSE, cache=TRUE, include=TRUE, results='asis'} 
# Create regression output table
labels <- c('Percent Perceived', 'Percent Fear',
            'Annual GDP Growth', 'Percent Opportunities', 'Percent Fear x Percent Opportunities','(Intercept)')

@@

```{r echo = FALSE, cache=TRUE, include=TRUE, results='asis'}
library(Zelig)

Z1 <- zelig(PercentIntention ~ PercentPerceived + PercentFear*PercentOpportunities + AnnualGDPGrowth, cite = FALSE,
            data = CompleteDataset, model = 'ls', param = function(z.out))

z5 <- zls$new()

summary(Z1)

Z1$sim()

sim(setz1)

@@
